Benchmarking the accelerated oblique random survival forest

### 2022-04-14 index.Rmd
bumping up number of runs to 50

The machine learning algorithms above are compared based on their discrimination (C-statistic) and scaled Brier score, which are computed using the `riskRegression` package, and specifically `riskRegression::Score()`. Computational time required for model fitting and model predictions are also presented. Results are averaged over 15 runs of Monte-Carlo Cross-validation. In each run of Monte-Carlo Cross-validation, the current data are separated into a training and testing set, all modeling techniques are applied to the training set, and model predictions are evaluated in the testing set.

@@

data_gt <- bm_vi_comb |>
  group_by(n_obs, xcorr, model) |> 
  summarize(
    across(
      .cols = c(overall, x, w, g, v),
      .fns = function(x) table_glue("{mean(x)} ({sd(x)})")
    )
  ) |> 
  ungroup() |> 
  mutate(
    xcorr = recode(
      xcorr, 
      '0.0' = '|Corr(linear effect variables, irrelevant variables)| = 0',
      '0.1' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.10',
      '0.2' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.20',
      '0.3' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.30',
      '0.4' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.40'),
    model = factor(
      model,
      levels = c('aorsf',
                 'aorsf_menze',
                 'xgboost',
                 'randomForestSRC',
                 'ranger'),
      labels = c('Negation importance',
                 'ANOVA importance',
                 'SHAP importance',
                 'Permutation importance (SRC)',
                 'Permutation importance (ranger)')
    )
  ) |> 
  select(model, overall, x, w, g, v) |> 
  arrange(model)

>>>>

The machine learning algorithms above are compared based on their discrimination (C-statistic) and scaled Brier score, which are computed using the `riskRegression` package, and specifically `riskRegression::Score()`. Computational time required for model fitting and model predictions are also presented. Results are averaged over 50 runs of Monte-Carlo Cross-validation. In each run of Monte-Carlo Cross-validation, the current data are separated into a training and testing set, all modeling techniques are applied to the training set, and model predictions are evaluated in the testing set.

@@

data_gt <- bm_vi_comb |>
  group_by(n_obs, xcorr, model) |> 
  summarize(
    across(
      .cols = c(overall, x, w, g, v),
      .fns = function(x) table_glue("{mean(x)}")
    )
  ) |> 
  ungroup() |> 
  mutate(
    xcorr = recode(
      xcorr, 
      '0.0' = '|Corr(linear effect variables, irrelevant variables)| = 0',
      '0.1' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.10',
      '0.2' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.20',
      '0.3' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.30',
      '0.4' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.40'),
    model = factor(
      model,
      levels = c('aorsf',
                 'aorsf_menze',
                 'xgboost',
                 'randomForestSRC',
                 'ranger'),
      labels = c('Negation importance',
                 'ANOVA importance',
                 'SHAP importance',
                 'Permutation importance (SRC)',
                 'Permutation importance (ranger)')
    )
  ) |> 
  select(model, overall, x, w, g, v) |> 
  arrange(model)
